---
title: "FF Research"
author: "Nick Olech"
date: "2024-05-06"
output: html_document
---

Fast Food Data set Research

## Step One - Load Required Data/Packages
```{r}
#Load the initial packages
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(readr)

#Read the dataset
fastfood <- read_csv("fastfood.csv")
head(fastfood)
```
##Step Two - Variable Analysis
```{r}
str(fastfood)
```
The variables in the dataframe are as follows:

Categorical: 
- restaurant: The name of the restaurant where the item is offered.
- item: The name of the fast food item.
- salad: classify whether the item is a salad or some other categorization related to salads.

Numerical:
- calories: The total number of calories in the item.
- cal_fat: Calories from fat in the item.
- total_fat: Total fat content of the item (in grams).
- sat_fat: Saturated fat content of the item (in grams).
- trans_fat: Trans fat content of the item (in grams).
- cholesterol: Cholesterol content of the item (in milligrams).
- sodium: Sodium content of the item (in milligrams).
- total_carb: Total carbohydrate content of the item (in grams).
- fiber: Dietary fiber content of the item (in grams).
- sugar: Total sugars in the item (in grams).
- protein: Protein content of the item (in grams).
- vit_a: Vitamin A content (percentage of daily value).
- vit_c:  Vitamin C content (percentage of daily value).
- calcium: Calcium content (percentage of daily value).

##Step Three - Question Proposal

Part one (Basic Questions):
How many restaurants are represented in this data set?
How many different total menu options still are there?
Which restaurants offer the most amount of options?
How many items exceed 20 grams of sugar?

Part two (Research Questions):
What is the relationship between total fat and caloric content?
What are the nutritional differences between items classified as "Salad" and others?
Can you identify any clusters of menu items based on nutritional content?

##Step Four - Data Sorting












