---
title: "FF Research"
author: "Nick Olech"
date: "2024-05-06"
output: html_document
---

Fast Food Data set Research

## Step One - Load Required Data/Packages
```{r}
#Load the initial packages
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(readr)

#Read the dataset
fastfood <- read_csv("fastfood.csv")
head(fastfood)
```
## Step Two - Variable Analysis
```{r}
str(fastfood)
```
The variables in the dataframe are as follows:

Categorical: 
- restaurant: The name of the restaurant where the item is offered.
- item: The name of the fast food item.
- salad: classify whether the item is a salad or some other categorization related to salads.

Numerical:
- calories: The total number of calories in the item.
- cal_fat: Calories from fat in the item.
- total_fat: Total fat content of the item (in grams).
- sat_fat: Saturated fat content of the item (in grams).
- trans_fat: Trans fat content of the item (in grams).
- cholesterol: Cholesterol content of the item (in milligrams).
- sodium: Sodium content of the item (in milligrams).
- total_carb: Total carbohydrate content of the item (in grams).
- fiber: Dietary fiber content of the item (in grams).
- sugar: Total sugars in the item (in grams).
- protein: Protein content of the item (in grams).
- vit_a: Vitamin A content (percentage of daily value).
- vit_c:  Vitamin C content (percentage of daily value).
- calcium: Calcium content (percentage of daily value).

## Step Three - Question Proposal

Part one (Basic Questions):
How many restaurants are represented in this data set?
How many different total menu options still are there?
Which restaurants offer the most amount of options?
How many items exceed 20 grams of sugar?

Part two (Research Questions):
What is the relationship between total fat and caloric content?
What are the nutritional differences between items classified as "Salad" and others?
Can you identify any clusters of menu items based on nutritional content?

## Step Four - Data Sorting

# Part (a), lets do some basic analysis of our data
I am concerned with useability of last column titled 'salad', so I want to make sure there are more than only one unique value

```{r}
# find how many unique values are in the column named 'salad'
Salad_count <- fastfood %>% 
      distinct(salad) %>%
       nrow()

# print the amount of unique values
print(Salad_count)
```
Before we sort, I also want to find out what calorie benchmark to sort by. This is just so menu items that are not typically ordered as entrees such as sides of dressing are not taken into account. 

```{r}
# sort the data frame from items with most calories to the least
fastfood_calorie_sorting <- fastfood %>% 
           arrange(desc(calories))

# print new table
print(fastfood_calorie_sorting)
```
```{r}
# graph to visualize how many items there are per caloric density
ggplot(data = fastfood_calorie_sorting, aes(x=calories)) +
  geom_histogram(binwidth = 150, fill ="blue", color = "black") + # we are going to put in bins of 150 calories
  labs(x = "Item", y = "Calories", title= "Calorie Content of Different Menu Items") + 
  theme_minimal()
```
```{r}
# lets look at which items appear in the first bin to see if they have relevance in our analysis
first_bin <- fastfood_calorie_sorting %>%
  filter(calories <= 150) %>%
  select(item, calories) #only show the calories

# show the new data
print(first_bin)
```
```{r}
# lets also just see how many restaurants there are in the set and how many recorded menu items are.
restaurant_description <- fastfood %>%
  group_by(restaurant) %>%
  summarise(Item_counts = n()) %>% 
  arrange(Item_counts)

# provide a visual to show what establishments are represented and how well they all are
ggplot(restaurant_description, aes(x = reorder(restaurant, Item_counts), y = Item_counts, fill = restaurant)) +
  geom_bar(stat = "identity", color = "black") +
  labs(x = "Restaurant", y = "Number of Menu Items", title = "Number of Menu Items per Restaurant") +
  theme_minimal()
```


# Part(b), before we filter our official data set that we will work with, lets recap what I have found.

There are 23 items that are below or equal to 150 calories, however all the items that are included are items that someone would  choose to eat as an entree or as a side. There is nothing included such as "side of ranch" or "salad dressing" which are items consumers would likely receive as a complementary side. This means that we can use every single entry in the data set

Another thing for sorting is that the column "salad" does not have any relevance in this data set, therefore it
would be wise to remove it

There are eight restaurants taken into account in this data frame with the amount of items accounted in each of them ranging from 27 to 115 different observations (aka menu items).

All values that may have been blank already are filled in with NA's, so there is no need to add that to our final sorted data set. 

# Part(c), do a little cleaning to make our workable dataset. 
















